\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{enumitem}

\title{\textbf{Quantum Coherence Ethics}\\[4pt] Canon Formalization}
\author{Power Corrupts}
\date{Draft --- February 2026}

\begin{document}
\maketitle

\begin{center}
\textit{A beam of white light enters the prism as a singularity.\\
The spectrum that emerges is what the light really looks like.}
\end{center}

\section{Foundations}

Quantum Coherence Ethics (QCE) is an ethical framework grounded in the many-worlds interpretation of quantum mechanics. It holds that:

\begin{enumerate}[label=(\roman*)]
\item A person is a \textbf{distributed being}---a single entity refracted across every branch of the wave function that shares its point of origin (DNA, spacetime coordinates, causal insertion).
\item The distributed being persists across branches in the way white light persists across the wavelengths of its spectrum: every wavelength \textit{is} the light.
\item Ethical weight arises not from freedom of choice---which is not required---but from the structural fact that present actions shape the statistical character of one's future distribution.
\item It looks like Copenhagen from the inside. It is Everett from the outside.
\end{enumerate}

\section{The Triple P}

For any future branch $\omega$, three quantities characterize the quality of existence within it:

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Symbol} & \textbf{Name} & \textbf{Measures} \\
\midrule
$P(\omega)$ & Probability & Lived existence as agent \\
$\Sigma(\omega)$ & Possibility & Scope of existence; degrees of freedom \\
$\Lambda(\omega)$ & Potential & Scale of existence; capacity to act \\
\bottomrule
\end{tabular}
\end{center}

\medskip
\textbf{Good} is that which increases Triple P across one's future distribution.\\
\textbf{Evil} is that which decreases it.

\subsection{Branch Weight}

Each future branch $\omega$ carries a branch weight $w(\omega\mid a)$: the share of the wave function's amplitude that flows into $\omega$ given present action $a$. This is the Born measure---an ontological quantity describing the structure of reality.

\textbf{Note.} The branch weight $w$ and the probability $P$ are both probabilities. They are different substances:
\begin{itemize}
\item $w(\omega\mid a)$ is \textit{ontological}---how much of reality flows into the branch.
\item $P(\omega)$ is \textit{epistemological}---an assessment of lived agentive presence within the branch.
\end{itemize}

\subsection{The Canon Equation}

Let $\Omega(a)$ denote the set of future branches reachable from present action $a$. Then:
\begin{equation}
\boxed{\;QCE(a)\;=\;\sum_{\omega\,\in\,\Omega(a)} w(\omega\mid a)\;\Big[\;P(\omega)\;\cdot\;\big(\,\Sigma(\omega)+\Lambda(\omega)\,\big)\,\Big]\;}
\end{equation}

\subsection{Dual Reading}

The canon equation admits two readings, corresponding to the inside and outside views of the same reality.

\paragraph{Copenhagen (inside view).}
The weights are Born probabilities summing to 1. The equation gives the expected Triple P from action $a$ as experienced from within a single branch:
\begin{equation}
QCE_{\textsc{c}}(a)\;=\;\mathbb{E}_{\,\omega}\Big[\,P(\omega)\cdot\big(\Sigma(\omega)+\Lambda(\omega)\big)\,\Big],\qquad \sum_{\omega}\,w(\omega\mid a)\;=\;1
\end{equation}

\paragraph{Everett (outside view).}
The weights are branch measures that grow with the branching structure over time. The sum is not constrained to 1. The equation gives the total Triple P across the full distributed being.
\begin{equation}
QCE_{\textsc{e}}(a)\;=\;\sum_{\omega\,\in\,\Omega(a)}\mu(\omega\mid a)\;\Big[\,P(\omega)\cdot\big(\Sigma(\omega)+\Lambda(\omega)\big)\,\Big],\qquad \sum_{\omega}\,\mu(\omega\mid a)\;\;\text{unbounded}
\end{equation}

Same equation. Different reading of the weight. Copenhagen from the inside; Everett from the outside.

\section{Action Selection}

\paragraph{Theoretical (Argmax).}
The theoretically optimal action maximizes $QCE$:
\begin{equation}
\boxed{\;a^{*}\;=\;\arg\max_{a}\;QCE(a)\;}
\end{equation}

\paragraph{Practical (Softmax).}
In practice, exact optimization is neither required nor desirable. A softmax distribution over actions is sufficient:
\begin{equation}
\boxed{\;\pi(a)\;=\;\frac{\exp\!\big(\beta\cdot QCE(a)\big)}{\displaystyle\sum_{a'}\exp\!\big(\beta\cdot QCE(a')\big)}\;}
\end{equation}
where $\beta>0$ is a temperature parameter. As $\beta\to\infty$, softmax collapses to argmax. As $\beta\to 0$, all actions become equiprobable.

\section{Principles}

\begin{enumerate}[label=\Roman*.]
\item \textbf{Quantum Morality.} Good is increasing Triple P across one's future distribution. Evil is decreasing it.
\item \textbf{The First Rule.} What is good for this goose is good for the gander.
\item \textbf{Non-Tyranny of the Present.} The present self holds no privileged authority over the distribution.
\item \textbf{Non-Judgment.} No single branch-self can judge another.
\item \textbf{Coherence as Product.} Coherence is not chosen. It is the emergent result of increasing Triple P without increasing constraints.
\item \textbf{The Multiplicative Function.} Branching multiplies the effects of present actions.
\item \textbf{The Structural Precondition.} QCE does not derive ought from is. It identifies Triple P as the structural ground of any ethical discourse.
\end{enumerate}

\section{Glossary}

\begin{tabular}{lp{10cm}}
\toprule
\textbf{Term} & \textbf{Definition} \\
\midrule
Distributed being & A single entity refracted across all branches sharing its origin. \\
Triple P & Probability, Possibility, Potential. \\
Branch weight ($w$) & Born measure. Ontological probability. \\
Probability ($P$) & Epistemological probability---lived agentive presence. \\
Possibility ($\Sigma$) & Scope. Degrees of freedom, open paths. \\
Potential ($\Lambda$) & Scale. Capacity, resources, power to act. \\
Agency & The distributed collective of agentive processes constituting a person. \\
Coherence & The emergent state of full spectral expression across branches. \\
Tyranny of the present & Any act foreclosing possibilities for the distributed being. \\
\bottomrule
\end{tabular}

\vfill
\begin{center}
\textit{The spectrum is most coherent when no wavelength is suppressed.}

\medskip
\textit{You are not making me more me by cutting away what I could possibly be.\\
By defining me you are delimiting me.}
\end{center}

\end{document}
